---
title: "the CLT"
author: "Thelma Means"
date: 'summer 2022'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")
kkmean=mean(KK_data)
kkstd=sd(KK_data)
```
The graph is not unimodal it has 2 peaks. no the peaks are not the same in size.
Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

mean and sd
`r kkmean`, `r kkstd`


Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
sampMean = mean(x.avg)
sampleSD = sd(x.avg)
densityplot(x.avg,main="sample size 2")
```

`r sampMean`, `r sampleSD`

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

 the graph is not unimodal. the graph has 3 peaks. all the peaks are not the same.

Do this again for 4 random samples



```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
sampMean = mean(x.avg)
sampleSD = sd(x.avg)
densityplot(x.avg,main="sample size 4")
```

`r sampMean`, `r sampleSD`
For this graph there are still 3 modes, center is getting higher

Then again for 9 random samples


```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
sampMean = mean(x.avg)
sampleSD = sd(x.avg)
densityplot(x.avg,main="sample size 9")
```

`r sampMean`, `r sampleSD`

The graph is unimodal. there are no peaks on the side





then 16 random samples


```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
sampMean = mean(x.avg)
sampleSD = sd(x.avg)
densityplot(x.avg,main="sample size 16")
```





The graph is showing that the peak is unimodal.






finally for 36 random samples.

```{r}
numb =36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
sampMean = mean(x.avg)
sampleSD = sd(x.avg)
densityplot(x.avg,main="sample size 36")
```

`r sampMean`, `r sampleSD`

Starting to look like a normal distribution. and has become unimodal


Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 

Then submit the link to your github project  to canvas to complete this assignment.